GVN-Hoist: Hoisting Computations from Branches

### 2016-08-23 hoist.tex
reword some more

The code-hoisting pass can be divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates to hoist and compute hoisting position,
\item check whether moving the code is legal and profitable,
\item transform the code.
\end{itemize}

\subsection{Finding the candidates}
The first step is to find a set of instructions that perform identical
computations: this is performed by a linear scan of all instructions of the
program and classifying all instructions by their value given by GVN.  The
current implementation of GVN in LLVM has some limitations when it comes to
loads and stores so we compute the GVN of loads and stores separately.  Our
short-time solution to value number loads is to hash the address from where the
value is to be loaded. For stores, we value number the address as well as the
value to be stored at that address.

@@

The process of computing GVN can be on-demand (as we come across an instruction)
or, precomputed (computing GVN of all the instructions beforehand). Which
process to choose is determined by the scope of code-hoisting we want to
perform. In a pessimistic approach (Section-\ref{subsec:pessimistic}) where we
want to hoist limited set of instructions from the sibling branches as we iterate
the DFS tree bottom-up, it is sufficient to compute values on-demand. Whereas,
in the optimistic approach (Section-\ref{subsec:optimistic}), where we want to
hoist as many instructions as possible, would require values to be precomputed.

Once the instructions have been classified in equivalence classes, we compute
for each group of equivalent instructions a point in the program that is both
legal and profitable for the code-hoisting.

>>>>

The code-hoisting pass can be divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates: instructions computing same values,
\item compute a point in the program where it is both legal and profitable to
  move the code,
\item transform the code.
\end{itemize}

\subsection{Finding the candidates}
The first step is to find a set of instructions that perform identical
computations: this is performed by a linear scan of all instructions of the
program and classifying all instructions by their value given by GVN.

The current implementation of GVN in LLVM has some limitations when it comes to
loads and stores so we compute the GVN of loads and stores separately.  Our
short-time solution to value number loads is to hash the address from where the
value is to be loaded. For stores, we value number the address as well as the
value to be stored at that address.

@@

The process of computing GVN can be on-demand (as we come across an instruction)
or, precomputed (computing GVN of all the instructions beforehand). Which
process to choose is determined by the scope of code-hoisting we want to
perform. In a pessimistic approach, as described in
Section-\ref{subsec:pessimistic}, we want to hoist a limited set of instructions
from the sibling branches as we iterate the DFS tree bottom-up, it is sufficient
to compute GVN values on-demand. Whereas, in the optimistic approach, as
described in Section-\ref{subsec:optimistic}, we want to hoist as many
instructions as possible, and it would require GVN values to be precomputed.

Once the instructions have been classified in equivalence classes, we compute
for each group of equivalent instructions a point in the program that is both
legal and profitable for the instructions to be moved to.
